Natural sources of vagueness and their implications

### 2017-10-27 book_chapter/paper.tex
Added discussion of results for loose interaction model. Cleaned up some plots.

Following this idea, we here survey proposals for addressing vagueness in the context of signaling games and reflect on their implications for how one thinks of rationality in the context of language use.
Before we start, we want to establish some vocabulary that will be useful later on.
%
%
%\section{Facets of rationality}
%\label{sec:facets-rationality}
%
Rationality is an elusive notion which is frequently debated in areas like philosophy, psychology, and economics.
Discussions around it, although touching on different aspects of the concept, often fail to clearly demarcate them.
We can start by considering what is deemed to be most important when characterizing the rationality of a given choice.
The aforementioned classical picture of language and meaning is focused on dichotomies like true and false, meaningful and meaningless, correct and incorrect.
A sentence can be true or false only if it is meaningful, and it is meaningful if it is constructed according to correct rules.
Rationality is intimately connected with the ability to follow good procedures, not only of sentence production, but ultimately of sentence combination and reasoning (think of what is required for making a logically valid deductive inference).
A \emph{procedural} account of rationality thus focuses on the means, rather than the ends.
One can also do the opposite and focus on the consequences instead.
\emph{Instrumental} rationality, as it is typically called, characterizes an agent's choice as rational if it maximizes the possibility of achieving a desired goal, regardless of the means.
The notion is linked to David Hume~\parencite*{hume_treatise_1738}, epitomized in his assertion that ``Reason is, and ought to only be the slave of the passions.''
Instrumental rationality is close to a notion of rational choice that is used in economics and game theory%
\footnote{In fact, it has been argued~\parencite{vanderschraaf_informal_1998} that Hume's whole account of convention is very closely in line with modern game theory.}%
: agents are rational if and only if they make decisions that maximize their expected utility.
A more in-depth discussion of the opposition in the context of theoretical economics can be found, for example, in the work of Herbert A.~Simon~\parencite*[\emph{e.g.}][]{simon_rationality_1986}%
\footnote{Simon uses the term substantive instead of instrumental rationality, but the characterization is basically the same~\parencite[210-212]{simon_rationality_1986}.}%
.
%Concretely, for a (finite) set of acts $A$, a (finite) set of world states $T$ with prior probability $P \in \Delta(T)$ and a utility function $u \colon A \times T \rightarrow \mathbb{R}$, choice of action $a$ is rational only if the expected utility $EU(a) = \sum_{t\in T} P(t) \, u(a,t)$ of $a$ is at least as high as that of any other $a' \in A$.\todo{Brings in a particular model too soon}
% The dichotomy between procedural and instrumental views of rationality is not an exclusive one, since usually both means and ends are taking into account, but it helps us describe where the emphasis is placed on.

@@

The expected utility $EU$ of a strategy can be calculated using the utility function and aggregating payoffs for all pairings of states of affairs and actions, weighted by the probability of each state. Concretely, the expected utility of $\sigma$ given $\rho$ is $EU_S(\sigma \mid \rho) = \sum_{t \in T} P(t) \ U_S(t, \rho(\sigma(t)))$ and the expected utility of $\rho$ given $\sigma$ is $EU_S(\rho \mid \sigma) = \sum_{t \in T} P(t) \ U_R(t, \rho(\sigma(t)))$.

@@

% EU(\sigma, \rho) = \sum_{t \in T} U(t, \rho(\sigma(t)))

@@

\section{How could language not be vague?}
\label{sec:finite-experience}

@@

In order to explore these considerations further, in the remainder of the paper we propose three variations of a multi-population model of imprecise imitation dynamics.
The idea is to investigate how populations with different levels of imprecision interact, and to what extent does the hypothesized temporary advantage of faster convergence helps vagueness to thrive in such an environment.

@@

Finally, the update probabilities for a sender strategy of type $\alpha$ at time instant $i+1$ is given by:
$$
\sigma_{i+1}^{\alpha}(m|t) \propto P_{o}^{\alpha}(m|t)EU_{\sigma_{i}}^{\alpha}(m,t,\rho_{i}^{\star})
$$
and similarly for a receiver strategy of type $\alpha$ by:
$$
\rho_{i+1}^{\alpha}(t|m) \propto P_{o}^{\alpha}(t|m)EU_{\rho_{i}}^{\alpha}(t,m,\sigma_{i}^{\star})
$$

The formulations so far cover the evolution of the particular strategies of agents.
We can think of this as the level of cultural evolution: agents are born with a certain level of imprecision and learn strategies based on the behavior of others.
Alongside this process, we can imagine another level of selection, where agents die and new agents are born.
More successful agents will have a higher likelihood of surviving and reproducing, giving rise to more agents with their level of imprecision.
Levels of imprecision are thus subject to an evolutionary dynamic that is indirectly influenced by the cultural dynamic.
\todo{genotype vs phenotype?}
Importantly, only the level of imprecision is passed on to new generations under this dynamic, not the actual strategies developed by the agents at the cultural level.

We model this process by changing the proportion of each type $P(\alpha)$ according to the replicator dynamic.
A population of type $\alpha$ consists of agents employing both a sender and a receiver strategy, thus the overall fitness of the population must involve the expected utilities of each.
We could imagine this process happening at a different speed than the cultural process, in which case we could have different time scales.
For the sake of simplicity, we choose to have them both happen at each time step, but calculate the changes occurring at this level of selection after the other level.
We define the proportion of type $\alpha$ at time step $i+1$ as:
$$
P_{i+1}(\alpha) \propto P_i(\alpha)(EU_{\sigma_{i+1}}^{\alpha}(m,t,\rho_{i}^{\star}) + EU_{\rho_{i+1}}^{\alpha}(t,m,\sigma_{i}^{\star}))
$$
In order to additionally account for the fact that strategies are not passed on to new generations, we mix the evolved strategies of a certain type $\sigma^\alpha$ and $\rho^\alpha$ with new random strategies $\tilde{\sigma}$ and $\tilde{\rho}$ according to a parameter $\gamma$ defining the birth rate within the population.
This can be described, for a certain time step $i+1$, in the following formulas:
$$
\sigma_{i+1}^{\alpha}(m|t)=(1 - \gamma)\sigma_{i+1}^{\alpha}(m|t) + \gamma \tilde{\sigma}
$$
$$
\rho_{i+1}^{\alpha}(t|m)=(1 - \gamma)\rho_{i+1}^{\alpha}(t|m) + \gamma \tilde{\rho}
$$

@@

The first thing to observe from the simulation results is that the population with no imprecision ($\alpha = 0$) always dominated the other populations in every run.
\begin{figure}
  \centering
  \begin{subfigure}[]{0.45\textwidth}
    \includegraphics[width=\textwidth]{simulation/results/round-3/plots/proportion-example-0-005-strong.png}
%    \caption{Crisp}
%    \label{fig:example_stratsA}
  \end{subfigure}
  \hfill
  \begin{subfigure}[]{0.45\textwidth}
    \includegraphics[width=\textwidth]{simulation/results/round-3/plots/proportion-example-0-005-01-strong.png}
%    \caption{Vague}
%    \label{fig:example_stratsB}
  \end{subfigure}
  \caption{\todo[inline]{description}}
  \label{fig:examples-proportion-tight-interaction}
\end{figure}
In Figure~\ref{fig:examples-proportion-tight-interaction} we plot the evolution of the proportion of each population in the two-population and three-populations scenario for one example trial.
There were no qualitative differences across trials.
As the plot shows, the population with no imprecision steadily increases its proportion against the others.
In the three population scenario, the proportion of the population with $\alpha = 0.05$ sees a slight increase in the beginning of the simulation, but inexorably starts a downward trend.

These observations go against the expectation of~\textcite{franke_vagueness_2017} that faster convergence to a convex strategy by populations with a certain level of imprecision could give them a temporary advantage to take over and eliminate other types.
What happens in this setup is nevertheless easy to explain.
Because the populations interact very tightly, they develop strategies in close tandem with each other.
One of the consequences of this is that the population with no imprecision reaps some benefits from evolving together with a population with a certain level of imprecision.
Namely, they reach convexity faster and develop more homogeneous strategies
\begin{figure}
  \centering
  \begin{subfigure}[]{0.3\textwidth}
    \includegraphics[width=\textwidth]{simulation/results/round-3/plots/convex-percentage-all-strong.png}
%    \caption{Crisp}
    \label{fig:convexity-tight-interaction}
  \end{subfigure}
  \hfill
  \begin{subfigure}[]{0.3\textwidth}
    \includegraphics[width=\textwidth]{simulation/results/round-3/plots/entropy-sender-all-strong.png}
%    \caption{Vague}
    \label{fig:entropy-sender-tight-interaction}
  \end{subfigure}
  \hfill
  \begin{subfigure}[]{0.3\textwidth}
    \includegraphics[width=\textwidth]{simulation/results/round-3/plots/entropy-receiver-all-strong.png}
%    \caption{Vague}
    \label{fig:entropy-receiver-tight-interaction}
  \end{subfigure}
  \caption{\todo[inline]{description}}
  \label{fig:metrics-tight-interaction}
\end{figure}
We can see the effect on convexity by looking to Figure~\ref{fig:convexity-tight-interaction} where we plot, for each scenario, the percentage of strategies that are convex at a given iteration, including the scenario with a population with no imprecision evolving on its own.
These effects preclude the hypothesized temporary advantage to even manifest itself.

@@

\section{Conclusion}
\label{sec:conclusion}

We tried to show that, if we pragmatically acknowledge the complex and dynamic environment that surrounds language learning and use, we find many plausible sources of uncertainty that can lead to vague signal use.
We supported this claim by giving an overview of recent research that tries to accommodate for vagueness in the context of sim-max games, and by discussing, in more general terms, how these considerations are relevant for reference games, and in the broader context of language as a multiplicity of language-games.
Furthermore, we argued that if we broaden our notion of rationality beyond mere maximization of expected utility, we also find reasons to welcome the positive aspects of these processes and to see their acceptance as a perfectly rational choice.
Irrational would be to ignore the finite nature of our existence and the constraints that condition language learning and use.
Our challenge as researchers is of course not only to draw attention to the possibilities, but also to characterize which particular constraints give rise to vague signal use and how.

>>>>

Following this idea, we here survey proposals for addressing vagueness in the context of signaling games and reflect on their implications for how one thinks of rationality in the context of language use.
Before we start, we want to establish some vocabulary that will be useful later on.
%
%
%\section{Facets of rationality}
%\label{sec:facets-rationality}
%
Rationality is an elusive notion which is frequently debated in areas like philosophy, psychology, and economics.
Discussions around it, although touching on different aspects of the concept, often fail to clearly demarcate them.
We can start by considering what is deemed to be most important when characterizing the rationality of a given choice.
The aforementioned classical picture of language and meaning is focused on dichotomies like true and false, meaningful and meaningless, correct and incorrect.
A sentence can be true or false only if it is meaningful, and it is meaningful if it is constructed according to correct rules.
Rationality is intimately connected with the ability to follow good procedures, not only of sentence production, but ultimately of sentence combination and reasoning (think of what is required for making a logically valid deductive inference).
A \emph{procedural} account of rationality thus focuses on the means, rather than the ends.
One can also do the opposite and focus on the consequences instead.
\emph{Instrumental} rationality, as it is typically called, characterizes an agent's choice as rational if it maximizes the possibility of achieving a desired goal, regardless of the means.
The notion is linked to David Hume~\parencite*{hume_treatise_1738}, epitomized in his assertion that ``Reason is, and ought to only be the slave of the passions.''
Instrumental rationality is close to a notion of rational choice that is used in economics and game theory%
\footnote{In fact, it has been argued~\parencite{vanderschraaf_informal_1998} that Hume's whole account of convention is very closely in line with modern game theory.}%
: agents are rational if and only if they make decisions that maximize their expected utility.
A more in-depth discussion of the opposition in the context of theoretical economics can be found, for example, in the work of Herbert A.~Simon~\parencite*[\emph{e.g.}][]{simon_rationality_1986}%
\footnote{Simon uses the term substantive instead of instrumental rationality, but the characterization is basically the same~\parencite[210-212]{simon_rationality_1986}.}%
.
%Concretely, for a (finite) set of acts $A$, a (finite) set of world states $T$ with prior probability $P \in \Delta(T)$ and a utility function $u \colon A \times T \rightarrow \mathbb{R}$, choice of action $a$ is rational only if the expected utility $\text{EU}(a) = \sum_{t\in T} P(t) \, u(a,t)$ of $a$ is at least as high as that of any other $a' \in A$.\todo{Brings in a particular model too soon}
% The dichotomy between procedural and instrumental views of rationality is not an exclusive one, since usually both means and ends are taking into account, but it helps us describe where the emphasis is placed on.

@@

The expected utility $\text{EU}$ of a strategy can be calculated using the utility function and aggregating payoffs for all pairings of states of affairs and actions, weighted by the probability of each state. Concretely, the expected utility of $\sigma$ given $\rho$ is $\text{EU}_S(\sigma \mid \rho) = \sum_{t \in T} P(t) \ U_S(t, \rho(\sigma(t)))$ and the expected utility of $\rho$ given $\sigma$ is $\text{EU}_S(\rho \mid \sigma) = \sum_{t \in T} P(t) \ U_R(t, \rho(\sigma(t)))$.

@@

% \text{EU}(\sigma, \rho) = \sum_{t \in T} U(t, \rho(\sigma(t)))

@@

\section{The ecology of vagueness}
\label{sec:finite-experience}

@@

In order to explore these considerations further, in the remainder of the paper we propose two variations of a multi-population model of imprecise imitation dynamics.
The idea is to investigate how populations with different levels of imprecision interact, and to what extent does the hypothesized temporary advantage of faster convergence helps vagueness to thrive in such an environment.

@@

Finally, the update probabilities for a sender strategy of type $\alpha$ at time instant $i+1$ is given by:
$$
\sigma_{i+1}^{\alpha}(m|t) \propto P_{o}^{\alpha}(m|t)\text{EU}_{\sigma_{i}}^{\alpha}(m,t,\rho_{i}^{\star})
$$
and similarly for a receiver strategy of type $\alpha$ by:
$$
\rho_{i+1}^{\alpha}(t|m) \propto P_{o}^{\alpha}(t|m)\text{EU}_{\rho_{i}}^{\alpha}(t,m,\sigma_{i}^{\star})
$$

The formulations so far cover the evolution of the particular strategies of agents.
We can think of this as the level of cultural evolution: agents are born with a certain level of imprecision and learn strategies based on the behavior of others.
Alongside this process, we can imagine another level of selection, where agents die and new agents are born.
More successful agents will have a higher likelihood of surviving and reproducing, giving rise to more agents with their level of imprecision.
Levels of imprecision are thus subject to an evolutionary dynamic that is indirectly influenced by the cultural dynamic.
%\todo{genotype vs phenotype?}
Importantly, only the level of imprecision is passed on to new generations under this dynamic, not the actual strategies developed by the agents at the cultural level.

We model this process by changing the proportion of each type $P(\alpha)$ according to the replicator dynamic.
A population of type $\alpha$ consists of agents employing both a sender and a receiver strategy, thus the overall fitness of the population must involve the expected utilities of each.
We could imagine this process happening at a different speed than the cultural process, in which case we could have different time scales.
For the sake of simplicity, we choose to have them both happen at each time step, but calculate the changes occurring at this level of selection after the other level.
We define the proportion of type $\alpha$ at time step $i+1$ as:
$$
P_{i+1}(\alpha) \propto P_i(\alpha)(\text{EU}_{\sigma_{i+1}}^{\alpha}(m,t,\rho_{i}^{\star}) + \text{EU}_{\rho_{i+1}}^{\alpha}(t,m,\sigma_{i}^{\star}))
$$
In order to additionally account for the fact that strategies are not passed on to new generations, we mix the evolved strategies of a certain type $\sigma^\alpha$ and $\rho^\alpha$ with new random strategies $\tilde{\sigma}$ and $\tilde{\rho}$ according to a parameter $\gamma$ defining the birth rate within the population.
This can be described, for a certain time step $i+1$, in the following formulas:
$$
\sigma_{i+1}^{\alpha}(m|t)=(1 - \gamma)\sigma_{i+1}^{\alpha}(m|t) + \gamma \tilde{\sigma}
$$
$$
\rho_{i+1}^{\alpha}(t|m)=(1 - \gamma)\rho_{i+1}^{\alpha}(t|m) + \gamma \tilde{\rho}
$$

@@

The first thing to observe from the simulation results is that the population with no imprecision ($\alpha = 0$) always dominated the other populations in every run.
\begin{figure}
  \centering
  \begin{subfigure}[]{\textwidth}
    \includegraphics[width=\textwidth]{simulation/results/round-3/plots/proportion-cases-0-005-strong.png}
    \caption{Two populations scenario.}
    \label{fig:proportion-cases-two-tight-interaction}
  \end{subfigure}
  \hfill
  \begin{subfigure}[]{\textwidth}
    \includegraphics[width=\textwidth]{simulation/results/round-3/plots/proportion-cases-0-005-01-strong.png}
    \caption{Three populations scenario.}
    \label{fig:proportion-cases-three-tight-interaction}
  \end{subfigure}
  \caption{Evolution of population proportions through time for each simulation trial of the tight interaction model.}
  \label{fig:proportion-cases-tight-interaction}
\end{figure}
In Figure~\ref{fig:proportion-cases-tight-interaction} we plot the evolution of the proportion of each population in the two-population and three-populations scenario for all trials.
As the plot shows, for every trial, the population with no imprecision steadily increases its proportion against the others.
In the three population scenario, the proportion of the population with $\alpha = 0.05$ sees a slight increase in the beginning of the simulation, but inexorably starts a downward trend.

These observations go against the expectation of~\textcite{franke_vagueness_2017} that faster convergence to a convex strategy by populations with a certain level of imprecision could give them a temporary advantage to take over and eliminate other types.
The reason for this is interesting in itself.
What happens is that, because of the tight interaction between populations, the strategies of each type evolve in close tandem with each other.
One of the consequences of this is that the population with no imprecision reaches convexity faster and develops more homogeneous strategies because of the interaction with the populations with imprecision.
We can see the effect on convexity by looking into the percentage of trials with convex sender strategies at a given iteration, for each scenario, and comparing the three scenarios: population with no imprecision evolving alone, two populations ($\alpha \in \{0, 0.05\}$), and three populations ($\alpha \in \{0, 0.05, 0.1\}$).
\begin{figure}
  \centering
  \begin{subfigure}[]{0.32\textwidth}
    \includegraphics[width=\textwidth]{simulation/results/round-3/plots/convex-percentage-all-strong.png}
    \caption{Percentage of convex sender strategies.}
    \label{fig:convexity-tight-interaction}
  \end{subfigure}
  \hfill
  \begin{subfigure}[]{0.32\textwidth}
    \includegraphics[width=\textwidth]{simulation/results/round-3/plots/entropy-sender-all-strong.png}
    \caption{Mean entropy of sender strategies.}
    \label{fig:entropy-sender-tight-interaction}
  \end{subfigure}
  \hfill
  \begin{subfigure}[]{0.32\textwidth}
    \includegraphics[width=\textwidth]{simulation/results/round-3/plots/entropy-receiver-all-strong.png}
    \caption{Mean entropy of receiver strategies.}
    \label{fig:entropy-receiver-tight-interaction}
  \end{subfigure}
  \caption{Development of some metrics through time for the $\alpha = 0$ population in each of three scenarios: evolving alone (`0'), with an $\alpha = 0.05$ population (`0/0.05'), and with an additional $\alpha = 0.1$ population (`0/0.05/0.1').}
  \label{fig:metrics-tight-interaction}
\end{figure}
This is plotted in Figure~\ref{fig:convexity-tight-interaction}.
What we see is more trials reaching convexity earlier for the multi-population scenarios when compared with the single-poulation scenario.
This effect precludes the hypothesized temporary advantage of imprecision to even manifest itself, but it can be seen as a positive influence on the population with no imprecision.

@@

\subsection{Loose population interaction}
\label{sec:loose-interaction-model}
In order to model a different type of interaction between populations in our multi-population model, we need to make changes to some formulations.
Any formula that is not redefined in this section should be assumed to be the same as used for the model in Section~\ref{sec:tight-interaction-model}.
The dynamic we want to model here is one where agents of a certain type $\alpha$ imitate and learn only from other agents of the same type.
First, if agents learn only within their population, the imitation dynamic needs to consider only the expected utility against agents of that population.
We thus define the following expected utilities for a sender of type $\alpha$:
$$
\text{EU}_{\sigma}^{\alpha}(m,t_{o},\rho^{\alpha})=\sum_{t_{a}}P_{\bar{o}}^{\alpha}(t_{a}|t_{o})\sum_{t_{r}}P_{\rho}^{\alpha}(t_{r}|m)U(t_{a},t_{r})
$$
and for a receiver of type $\alpha$:
$$
\text{EU}_{\rho}^{\alpha}(t_{i},m,\sigma^{\alpha})=\sum_{t_{a}}P_{\bar{\sigma}}^{\alpha}(t_{a}|m)\sum_{t_{r}}P_{r}^{\alpha}(t_{r}|t_{i})U(t_{a},t_{r})
$$
The main difference is that these expected utilities are not calculated against all populations ($\sigma^\star$ and $\rho^\star$) but only against the agent's own type.

We can redefine the probability that a sender of type $\alpha$ observes a randomly sampled agent play message $m$ for observed state $t_o$ as:
$$
P_{o}^{\alpha}(m|t_{o})=\sum_{t_{a}}P_{\bar{o}}^{\alpha}(t_{a}|t_{o})P_{\sigma}^{\alpha}(m|t_{a})
$$
and the probability that a receiver of type $\alpha$ observes a randomly sampled agent choose interpretation $t_o$ given message $m$ as:
$$
P_{o}^{\alpha}(t_{o}|m)=\sum_{t_{r}}P_{o}^{\alpha}(t_{o}|t_{r})P_{\rho}^{\alpha}(t_{r}|m)
$$
Again, the main difference is that agents make observations within their own population, so to model a randomly sampled agent one needs only to take into account the same type.

Update probabilities for a sender strategy of type $\alpha$ at time instant $i+1$ is then given by:
$$
\sigma_{i+1}^{\alpha}(m|t) \propto P_{o}^{\alpha}(m|t)\text{EU}_{\sigma_{i}}^{\alpha}(m,t,\rho_{i}^{\alpha})
$$
and similarly for a receiver strategy of type $\alpha$ by:
$$
\rho_{i+1}^{\alpha}(t|m) \propto P_{o}^{\alpha}(t|m)\text{EU}_{\rho_{i}}^{\alpha}(t,m,\sigma_{i}^{\alpha})
$$

The selection process between different populations still follows the same motivation: agents of a certain type that evolve successful strategies (with respect to other types) will be more likely to survive and reproduce, benifitting the proportion of their population.
The formulation of the dynamic of the proportion of each type $P(\alpha)$ thus stays the same.
In order to avoid confusion, we want to stress that this means that these calculations thus still rely on the calculation of expected utilities across populations (\emph{i.e.}~$\text{EU}_{\sigma}^{\alpha}(m,t_{o},\rho^{\star})$ and $\text{EU}_{\rho}^{\alpha}(t_{i},m,\sigma^{\star})$) and not the newly introduced $\text{EU}_{\sigma}^{\alpha}(m,t_{o},\rho^{\alpha})$ and $\text{EU}_{\rho}^{\alpha}(t_{i},m,\sigma^{\alpha})$.

We ran the same number of simulation trials under the same conditions as for the model with tight population interaction.
\begin{figure}
  \centering
  \begin{subfigure}[]{\textwidth}
    \includegraphics[width=\textwidth]{simulation/results/round-3/plots/proportion-cases-0-005-weakest.png}
    \caption{Two populations scenario.}
    \label{fig:proportion-cases-two-loose-interaction}
  \end{subfigure}
  \hfill
  \begin{subfigure}[]{\textwidth}
    \includegraphics[width=\textwidth]{simulation/results/round-3/plots/proportion-cases-0-005-01-weakest.png}
    \caption{Three populations scenario.}
    \label{fig:proportion-cases-three-loose-interaction}
  \end{subfigure}
  \caption{Evolution of population proportions through time for each simulation trial of the loose interaction model.}
  \label{fig:proportion-cases-loose-interaction}
\end{figure}
In Figure~\ref{fig:proportion-cases-loose-interaction} we plot the evolution of population proportions for all trials of the multi-population scenarios.
The first thing to observe is that proportions evolve faster than in the model with tight interaction.
Whereas in the latter no given population ever reached much more than 70\% proportion, in this model we see that many trials resulted in the one population fully dominating the others.
In the two-population scenario, some population reached 99\% proportion in 24 out of 25 trials.
In the three-population scenario, this happened in 18 out of 25 trials.
Given that strategies no longer develop in close tandem with each other, differences in expected utility can be more salient resulting in some population reaching a more clear advantage than the other.

More interestingly for our investigation, some trials actually resulted in a population with some degree of imprecision dominating the others.
For the two-population scenario, $\alpha = 0.05$ fully reached 100\% proportion in 8 trials, a point from which it is technically impossible for the other population to recover.
In most cases the dominating population gains its ground from the start, but in 5 cases we see a temporary advantage of $\alpha = 0.05$ that is then lost to the other population.
In one interesting trial (85), $\alpha = 0.05$ reached 99.87\% only to then start losing ground to $\alpha = 0$.
For the three population scenario, $\alpha = 0.05$ fully reached 100\% proportion in only 1 trial and $\alpha = 0.1$ never reached more than 59\%.
In 5 other trials we see a positive trend for $\alpha = 0.05$, but given the reversals that sometimes occur (\emph{e.g.}~trial 171), one cannot be sure whether full dominance would be achieved if the simulation was left to run for longer time.

\section{Conclusion}
\label{sec:conclusion}
\todo[inline]{Extend/Rewrite}
We tried to show that, if we pragmatically acknowledge the complex and dynamic environment that surrounds language learning and use, we find many plausible sources of uncertainty that can lead to vague signal use.
We supported this claim by giving an overview of recent research that tries to accommodate for vagueness in the context of sim-max games, and by discussing, in more general terms, how these considerations are relevant for reference games, and in the broader context of language as a multiplicity of language-games.
Furthermore, we argued that if we broaden our notion of rationality beyond mere maximization of expected utility, we also find reasons to welcome the positive aspects of these processes and to see their acceptance as a perfectly rational choice.
Irrational would be to ignore the finite nature of our existence and the constraints that condition language learning and use.
Our challenge as researchers is of course not only to draw attention to the possibilities, but also to characterize which particular constraints give rise to vague signal use and how.
